### 2017-05-11 manuscript/usses_water_ms.Rmd
adds some analysis ANOVA details

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
---

@@

\Large{\textbf{Ecosystem and community resistance to six years of drought and deluge in the Sagebrush Steppe}}

@@

Drought and irrigation treatments were designed to decrease and increase the amount of ambient precipitation by 50\%, respectively.
To achieve this, we used a system of rain-out shelters and automatic irrigation [@Gherardi2013].
The rain-out shelters consisted of transparent acrylic shingles 1-1.5 m above the ground that covered an area of 2.5 by 2 m.
The shingles intercepted approximately 50\% of incoming rainfall, which was channeled into 75 liter containers.
Captured rainfall was then pumped out of the containers and sprayed on to the adjacent irrigation plot via two suspended sprinklers.
Pumping was triggered by float switches once water levels reached about 20 liters.
We disconnected the irrigation pumps each fall and reconnected them, often with difficulty, each spring.
The rain-out shelters remained in place throughout the year.

@@

### Data Analysis
####  ANPP and Ecosystem Stability

>>>>

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: false
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black
---

@@

\Large{\textbf{Ecosystem and community resistance to five years of drought and deluge in the Sagebrush Steppe}}

@@

Drought and irrigation treatments were designed to decrease and increase the amount of ambient precipitation by 50\%, respectively.
To achieve this, we used a system of rain-out shelters and automatic irrigation [@Gherardi2013].
The rain-out shelters consisted of transparent acrylic shingles 1-1.5 m above the ground that covered an area of $2.5\times2$ m.
The shingles intercepted approximately 50\% of incoming rainfall, which was channeled into 75 liter containers.
Captured rainfall was then pumped out of the containers and sprayed on to the adjacent irrigation plot via two suspended sprinklers.
Pumping was triggered by float switches once water levels reached about 20 liters.
We disconnected the irrigation pumps each fall and reconnected them, often with difficulty, each spring.
The rain-out shelters remained in place throughout the year.

@@

### Data Analysis
####  ANPP and Ecosystem Stability
We used ANOVA with treatment, year, and treatment$\times$year terms to test the effects of the treatments on ANPP over the course of the five year experiment.
To test for within-year differences of ANPP among treatments, we fit ANOVAs independently for each year with treatment terms only.
We used the \texttt{lm()} function in \texttt{R} [v3.3.2, @R2016] to fit the models, and the \texttt{anova()} function to extract sums-of-squares tables.
